### 2021-06-27 code/manuscript.Rmd
Remove single trials

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0(
    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
  ) %>%
    set_names(c("logRT", "P1", "N170", "N400")),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

>>>>

# File names for easier I/O
fnames <- list(
  montage = "results/montage.csv",
  objects_per_condition = "results/obj-per-cond.csv",
  trials = "results/trials.csv",
  ave_grand = "results/ave_grand.csv",
  ave_tfr_flat = "results/ave-tfr_flat.csv",
  ave_tfr_diff = "results/ave-tfr_diff.csv",
  models_lme = "results/models_lme.RDS",
  models_brm = paste0(
    "results/model_brm_", c("logRT", "P1", "N170", "N400"), ".RDS"
  ) %>%
    set_names(c("logRT", "P1", "N170", "N400")),
  model_brm_prior = "results/model_brm_prior.RDS"
)
```

@@

  # Combine single trial data for all subjects
  paste0("data/preprocessed/", subject_id, "_trials.csv") %>%
    map(read_csv, col_types = cols()) %>%
    bind_rows() %>%
    write_csv(fnames$trials)
